Merge_MCGrowthData

### 2024-04-03 Code/Merge_MCGrowthData.Rmd
Added missing data and reprocessed run #78. Regnerated GAM and plots
Fixed annotation for a variable

GrowthFlagError <- 0.2     # percentage of mu that std error must be less than

@@

# Save Long DF for GAM and Nested for further analysis 
```{r save files}

>>>>

GrowthFlagError <- 0.2     # What fraction of mu to determine if the growth fit is accepted relative to the std error.

@@

# Save Nested for further analysis 
```{r save files}
